Data Exploration

### 2018-11-26 src/data_exploration.Rmd
env. correlate boxplots per month and per year

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("plyr", "graphics") 
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
presence <- read.csv("../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno_env.csv", header = TRUE)
head(presence)
```

@@

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("plyr", "graphics", "ggplot2") 
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
presence <- read.csv("../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno_env_naocor_cels.csv", header = TRUE)
head(presence)
```

@@

```{r}
hist(presence$temp_dept, main = "Temp at Depth", xlab = "Kelvin")
dev.copy(png, "../output/env/simple_plots/temperature_depth_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

```{r}
boxplot(presence$temp_depth ~ presence$month, xlab = "month", ylab = "Temperature (Kelvin)", main = "Temperature at Observation Depth per Month")
dev.copy(png, "../output/env/simple_plots/temperature_boxplot_dept_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
boxplot(presence$chl_depth ~ presence$month, xlab = "month", ylab = "Chlorophyll Concentrations (mmol.m-3)", main = "Chlorophyll at Observation Depth per Month")
dev.copy(png, "../output/env/simple_plots/chlorophyll_boxplot_dept_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
boxplot(presence$salinity_depth ~ presence$month, xlab = "month", ylab = "Salinity Practical Salinity Unit (PSU)", main = "Salinity at Observation Depth per Month")
dev.copy(png, "../output/env/simple_plots/salinity_boxplot_dept_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

o2

xxxx
```{r}
boxplot(presence$temp_depth ~ presence$year, xlab = "Year", ylab = "Temperature (Kelvin)", main = "Temperature at Observation Depth")
dev.copy(png, "../output/env/simple_plots/temperature_boxplot_dept_year.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
